---
title: "ESM 206/244 GitHub Testing"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<<<<<<< HEAD
Type your name (or anything else) HERE: Liviu Iancu heyooooooooooooooooooooooooooo
=======
Type your name (or anything else) HERE: 
>>>>>>> 84c3d723a45389f013f87a9432ab439cabe25499

Here's some code (change the variable names and values):
```{r}
# Change these variable names and values:

<<<<<<< HEAD
green <- 99

pink <- 33

some_gross_mix_of_green_and_pink <- green/pink

=======
blue <- 10

red <- 15

purple <- blue/red
>>>>>>> 84c3d723a45389f013f87a9432ab439cabe25499

```

After making minimal changes, SAVE this .Rmd (default will be to the project folder, but check to make sure).

Notice that if you click on the 'Git' tab (up by the Environment tab), now your newly created Project (.Rproj) and updated .Rmd are there (along with, probably, a gitignore file that you don't really need to worry about).

Stage, commit, and push your updates back to github (see the step-by-step document).